---
title: "Assingment NYC Flight Data"
author: "Nikolai Litavr"
date: "October 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. 
In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, 
`airports.csv`, `planes.csv` and `weather.csv`.  Join/merge these tables such 
that there is one rectangular table with one row for each flight. 


Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
library(readr)

setwd("~/mycode/csx460/02-building-blocks/02-exercise-nycflights/data/")

airports <- read_csv("airports.csv")
flights <- read_csv("flights.csv")
planes <- read_csv("planes.csv")
weather <- read_csv("weather.csv")
```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
library(ggplot2)
arrivalDelays <- qplot(flights$arr_delay, geom="histogram", main="Arrival Delays for NYC flights", xlab = "Arrival Delay in Minutes", ylab = "Count", binwidth = 100, ylim = c(0, 300000))
arrivalDelays
departureDelays <- qplot(flights$dep_delay, geom="histogram", main="Departure Delays for NYC flights", xlab = "Departure Delays in Minutes", ylab = "Count", binwidth = 100)
departureDelays
```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
flights$date <- as.Date(with(flights, paste(year, month, day,sep="-")), "%Y-%m-%d")
scatterPlot <- qplot(date, xlab = "Date", ylab = "Arrival Delay")
scatterPlot
```



## Create tables for Categorical Variables

Create a `table`, counting the flights by origin airports and carrier.

```{r}
flightsTbl <- count(flights, c('origin', 'carrier'))
flightsTbl
```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}

```



